Summary

### 2015-10-23 inst/examples/summary.Rmd
Rmd update

---
title: "Summary"
author: "Niko Ilomäki"
date: "Tuesday, March 3, 2015"
output: markdown_document
---

# Summary of the preprocessed Fennica data

@@

df <- readRDS("df.Rds")

>>>>

---
title: "Summary"
author: "Niko Ilomäki and Leo Lahti"
date: "Tuesday, October 20, 2015"
output: markdown_document
---

# Fennica summary

@@

# Read the preprocessed data
df <- readRDS("df.Rds")
